A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-15 src/paper.tex
WIP: changes in figure and itv device definition

Initially, the CP infrastructure must provide an authentication mechanism so that viewers and STBs can be authenticated to use the secondary screen services. The STB must be authenticated in the application hosted on the CP infrastructure. Once the STB is authenticated, the viewers in the TV environment must link their user accounts with the STB. As a result, the viewer can use their personal device as a secondary screen for that STB, enabling the capture of viewers' interactions.

The architecture to accurately capture viewers interactions is shown in Figure~\ref{fig_architecture}. This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) a set-top box (STB), and the CP infrastructure (which includes an application hosting infrastructure). The green arrows represent the data flowing from the viewer to the CP infrastructure, while blue arrows denote the flow from CP infrastructure to the viewers. The black arrows represent the data flow inside the CP infrastructure.

>>>>

Initially, the CP infrastructure must provide an authentication mechanism so that viewers and their interactive TV (iTV) devices (e.g., set-top boxes or smart TVs) can be authenticated by the CP in order to use the secondary screen services. Once one iTV device is authenticated, the viewers in the TV environment must link their user accounts with the iTV device. As a result, the viewer can use their personal device as a secondary screen for that iTV device, enabling the capture of viewers' interactions.

The architecture to accurately capture viewers interactions is shown in Figure~\ref{fig_architecture}. This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) an iTV device, and the CP infrastructure (which includes an application hosting infrastructure). The green arrows represent the data flowing from the viewer to the CP infrastructure, while blue arrows denote the flow from CP infrastructure to the viewers. The black arrows represent the data flow inside the CP infrastructure.
